The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-17 draft/ms.tex
Summary section done and abstract

\title{The Exoplanet Orbit Database 2, 2014 updates}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
\end{abstract}

@@

We have had two major updates since \cite{Wright2011}. First, we
changed the scope of the EOD. We removed the limit on the type of the
host star. We included the planets discovered by various methods
(e.g. timing) in the EOD. We also have added some new fields, removed
obsolete fields and revised them as necessary.

Second, we included Kepler planet candidates and other planets on
exoplanets.org. Although they are not included in the EOD, we reported
them on our website to help the users explore them and use them
easily.

@@

We hope to include images of directly imaged planets (where allowed under copyright law) and
light curves for transits in the future.

>>>>

\title{The Exoplanet Orbit Database \textsc{II}: 2014 updates}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD). The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.

 Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
\end{abstract}

@@

We have had two major updates since \cite{Wright2011}. First, we
expanded the scope of the EOD. We removed the requirement for the host star being normal and included the planets discovered not only by RV and transit but also by various other methods (e.g. timing) in the EOD. We also have added some new fields, most notably, we now report the secondary eclipse depths. We removed obsolete fields and revised some fields as necessary.

Second, we included KOIs and other planets (the ones detected by microlensing, imaging, timing, and in the future, astrometry) on exoplanets.org. Although they are not included in the EOD, we reported them on our website since the users might find them useful for purposes of statistical studies and comparison.

@@

In the future, we hope to include images of directly imaged planets (where allowed under copyright law) and
light curves for transits. We also plan to display RV curves whenever their RV data are available.
